\documentclass{letter}
\usepackage[margin=1in]{geometry}
\usepackage{block}
\signature{Blair Urish}
\address{Blair Urish \\ Kansas State University \\ Department of Computer Science \\ Manhattan, KS 66505}

\begin{document}

\begin{letter}{Dr. William Hsu \\ Professor \\ Kansas State University \\ 2164 Engineering Hall \\ Manhattan, KS 66505}
\opening{Dear Dr. Hsu:}

Enclosed is my literature review entitled ``A literature review of Internet of Things security.'' The report synthesizes the literature
surrounding the security risks facing the Internet of Things. The report also discusses security standards that are being considered to 
mitigate the identified security risks. Finally, the report discusses government action to address Internet of Things security risks.\\
~\newline
In the report's discussion of the security risks, the literature identified risks in every layer of the Internet of Things architecture. 
These risks include distributed denial of service, unauthorized access, and many others. To address these risks, the literature outlined the need
for a standardized security stack. Some of the protocols discussed include Datagram Transport Layer Security (DTLS) and the Host Identity Protocol (HIP).
Of the two protocols, HIP was found to be more efficient, but DTLS provided better compatibility with existing networks. The literature provided
extensions to both protocols in order to address the various shortcomings in each protocol. Finally, the enclosed report discusses how the U.S. government
and European Union are addressing Internet of Things security risks. In the U.S., the FTC has not recommended any additional regulation, but does recommend
that Congress enact general cyber security regulation. In the European Union, a labeling requirement was proposed that would identify if a device meets
security standards.\\
~\newline
I appreciate you taking the time to read my report. If you have any questions or comments about the report, please feel free to contact me by email at
burace17@ksu.edu. 

\closing{Sincerely,}

\end{letter}
\end{document}
